---
title: "CCA metadata merge"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---
```{r setup, include=F}
library(tidyverse)
options("stringsAsFactors" = FALSE)
```

This notebook takes the cleaned metadata from Dean, and our additions, and creates a master table which contains merged, tree-level metadata from CCA planting, maternal voucher collection, and Dean's taxonomy.

## Load and merge metadata

```{r}
coe = read.csv("originals/DNTaxonomyCleaned.csv")
cca = read.csv("originals/CCATreesCleaned.csv")
dnvouch = read.csv("originals/DNVoucherRecordsCleaned.csv")
```

```{r}
cca_meta = cca %>%
  left_join(dnvouch, by="DNNumber") %>%
  mutate(CurrentName = trimws(CurrentName)) %>% 
  filter(!is.na(CurrentName)) %>%
  left_join(coe, by=c("CurrentName"="Binomial")) %>%
  select(FieldID, RowTree, CurrentName, everything())
```

How many CCA trees can't be matched to Dean's voucher data?

```{r}
table(!cca$DNNumber %in% dnvouch$DNNumber)
```

And how many trees have names which don't match the current taxonomy?

```{r}
table(!cca$CurrentName %in% coe$Binomial)
```


The union of these is:

```{r}
table(!cca$CurrentName %in% coe$Binomial | !cca$DNNumber %in% dnvouch$DNNumber)
```

## Write out current merged metadata
```{r}
write_csv(cca_meta, "CCATreesCombinedMetadata.csv")
```


# Investigate non-matching scientific names

```{r}
fullcoe = read.csv("originals/classification/FullCleanedTaxonomy.csv")
```

```{r}
nomatch = cca_meta %>% 
  filter(! CurrentName %in% fullcoe$CleanedBinomial) %>% 
  rowwise() %>%
  mutate(
    match.binom=paste(fullcoe$CleanedBinomial[
      agrep(CurrentName, fullcoe$CleanedBinomial, fixed=T)
      ], collapse="|"),
    match.synonym=paste(fullcoe$Synonyms[
      agrep(sub("^Eucalyptus |^Angophora |^Corymbia", "", CurrentName),
            fullcoe$Synonyms, fixed=T)
      ], collapse="|")
    ) %>%
  select(CurrentName, match.binom, match.synonym) %>%
  unique()
```

```{r}
nomatch2 = cca_meta %>% 
  filter(! CurrentName %in% fullcoe$CleanedBinomial) %>% 
  select(CurrentName, FieldID) %>%
  nest(FieldID) %>%
  mutate(
     spp.abbrev = sub("^(E)ucalyptus |^(A)ngophora |^(C)orymbia",
                      "\\1\\2\\3. ", CurrentName),
     spp.trim = sub("^(E)ucalyptus |^(A)ngophora |^(C)orymbia",
                    "", CurrentName),
     match.binom = map(CurrentName, function(cn) {
       m = agrep(cn, fullcoe$CleanedBinomial, fixed=T)
       if(length(m) == 0) {
         return(NULL)
       }
       return(fullcoe[m,c("CleanedBinomial", "Synonyms")])
     }),
     match.synonym = map(spp.abbrev, function(cn) {
       m = agrep(cn, fullcoe$Synonyms, fixed=T)
       if(length(m) == 0) {
         return(NULL)
       }
       return(fullcoe[m,c("CleanedBinomial", "Synonyms")])
     })
  )
```